Mission-time LTL (MLTL) Formula Validation Via Regular Expressions\thanks{Work supported in part by [omitted for blind review] {\bf Note that all references to appendices will be replaced with URLs in the final paper; they are appendices only for blind review.}}

### 2022-10-13 paper/Paper.tex
increased figure title and axis font sizes

    \includegraphics[scale=0.39]{images/Sim1Length.png}

@@

    \includegraphics[scale=0.39]{images/Sim1Time.png}

@@

    \includegraphics[scale=0.39]{images/Sim2Length.png}

@@

    \includegraphics[scale=0.39]{images/Sim2Time.png}

@@

    \includegraphics[scale=0.39]{images/Sim3Length.png}

@@

    \includegraphics[scale=0.39]{images/Sim3Time.png}

@@

    \includegraphics[scale=0.39]{images/Sim4Length.png}

@@

    \includegraphics[scale=0.39]{images/Sim4Time.png}

@@

    %Nodes
    \node[emptynode](inputs){vector reg\_phi, integers a, b, n};
    \node[node](initialize)[below=of inputs]{Initialize string pre, vector Comp};
    \node[node](loop)[below=2cm of initialize]{Update Comp};
    \node[node](empty)[left=of loop]{return \{\}};
    \node[node](return)[below=of loop]{return pre + Comp};
    \node[emptynode](loop_text)[right=1.1cm of loop]{for $i \in [1, \text{b}-\text{a}]$};
    \node[emptynode](placeholder)[below=0.5cm of initialize]{};
    \node[emptynode](empty_text)[rotate=30, left=1.3cm of placeholder]{If a$>$b};

@@

    %Nodes
    \node[emptynode](inputs){vector reg\_phi, integers a, b, n};
    \node[node](initialize)[below=of inputs]{Initialize string pre, vector Comp};
    \node[node](loop)[below=2cm of initialize]{Update Comp};
    \node[node](empty)[left=of loop]{return \{$S^n$\}};
    \node[node](return)[below=of loop]{return pre + Comp};
    \node[emptynode](loop_text)[right=1.1cm of loop]{for $i \in [1, \text{b}-\text{a}]$};
    \node[emptynode](placeholder)[below=0.5cm of initialize]{};
    \node[emptynode](empty_text)[rotate=30, left=1.3cm of placeholder]{If a$>$b};

@@

    %Nodes
    \node[emptynode](inputs){vector reg\_phi, reg\_psi and integers a, b, n};
    \node[node](initialize)[below=of inputs]{Initialize vector Comp};
    \node[node](loop)[below=2cm of initialize]{Update Comp};
    \node[node](empty)[left=of loop]{return \{\}};
    \node[node](return)[below=of loop]{return Comp};
    \node[emptynode](loop_text)[right=1.1cm of loop]{for $i \in [\text{a}, \text{b}-1]$};
    \node[emptynode](placeholder)[below=0.5cm of initialize]{};
    \node[emptynode](empty_text)[rotate=30, left=1.3cm of placeholder]{If a$>$b};

@@

    %Nodes
    \node[emptynode](inputs){vector reg\_phi, reg\_psi and integers a, b, n};
    \node[node](initialize)[below=of inputs]{Initialize vector Comp};
    \node[node](loop)[below=2cm of initialize]{Update Comp};
    \node[node](empty)[left=of loop]{return \{$S^n$\}};
    \node[node](return)[below=of loop]{return Comp};
    \node[emptynode](loop_text)[right=1.1cm of loop]{for $i \in [\text{a}, \text{b}-1]$};
    \node[emptynode](placeholder)[below=0.5cm of initialize]{};
    \node[emptynode](empty_text)[rotate=30, left=1.3cm of placeholder]{If a$>$b};

>>>>

    \includegraphics[scale=0.38]{images/Sim1Length_large.png}

@@

    \includegraphics[scale=0.38]{images/Sim1Time_large.png}

@@

    \includegraphics[scale=0.38]{images/Sim2Length_large.png}

@@

    \includegraphics[scale=0.38]{images/Sim2Time_large.png}

@@

    \includegraphics[scale=0.38]{images/Sim3Length_large.png}

@@

    \includegraphics[scale=0.38]{images/Sim3Time_large.png}

@@

    \includegraphics[scale=0.38]{images/Sim4Length_large.png}

@@

    \includegraphics[scale=0.38]{images/Sim4Time_large.png}

@@

    %Nodes
    \node[emptynode](inputs){vector reg\_phi, integers a, b, n};
    \node[node](initialize)[below=of inputs]{Initialize string pre, vector Comp};
    \node[node](loop)[below=2cm of initialize]{Update Comp};
    \node[node](empty)[left=of loop]{return \{\}};
    \node[node](return)[below=of loop]{return pre + Comp};
    \node[emptynode](loop_text)[right=1.1cm of loop]{for $i \in [1, \text{b}-\text{a}]$};
    \node[emptynode](placeholder)[below=0.5cm of initialize]{};
    \node[emptynode](empty_text)[rotate=36, left=1.3cm of placeholder]{If a$>$b};

@@

    %Nodes
    \node[emptynode](inputs){vector reg\_phi, integers a, b, n};
    \node[node](initialize)[below=of inputs]{Initialize string pre, vector Comp};
    \node[node](loop)[below=2cm of initialize]{Update Comp};
    \node[node](empty)[left=of loop]{return \{$S^n$\}};
    \node[node](return)[below=of loop]{return pre + Comp};
    \node[emptynode](loop_text)[right=1.1cm of loop]{for $i \in [1, \text{b}-\text{a}]$};
    \node[emptynode](placeholder)[below=0.5cm of initialize]{};
    \node[emptynode](empty_text)[rotate=36, left=1.3cm of placeholder]{If a$>$b};

@@

    %Nodes
    \node[emptynode](inputs){vector reg\_phi, reg\_psi and integers a, b, n};
    \node[node](initialize)[below=of inputs]{Initialize vector Comp};
    \node[node](loop)[below=2cm of initialize]{Update Comp};
    \node[node](empty)[left=of loop]{return \{\}};
    \node[node](return)[below=of loop]{return Comp};
    \node[emptynode](loop_text)[right=1.1cm of loop]{for $i \in [\text{a}, \text{b}-1]$};
    \node[emptynode](placeholder)[below=0.5cm of initialize]{};
    \node[emptynode](empty_text)[rotate=36, left=1.3cm of placeholder]{If a$>$b};

@@

    %Nodes
    \node[emptynode](inputs){vector reg\_phi, reg\_psi and integers a, b, n};
    \node[node](initialize)[below=of inputs]{Initialize vector Comp};
    \node[node](loop)[below=2cm of initialize]{Update Comp};
    \node[node](empty)[left=of loop]{return \{$S^n$\}};
    \node[node](return)[below=of loop]{return Comp};
    \node[emptynode](loop_text)[right=1.1cm of loop]{for $i \in [\text{a}, \text{b}-1]$};
    \node[emptynode](placeholder)[below=0.5cm of initialize]{};
    \node[emptynode](empty_text)[rotate=36, left=1.3cm of placeholder]{If a$>$b};
